Quantum Magic Games

### 2023-07-06 paper/main.tex
paper => refactor

\maketitle
\begin{abstract}
  \textbf{TODO}
\end{abstract}

@@

\paragraph{Outline of this paper.}
In Section~\ref{sec:magic-square}, we detail the intrinsics of the
magic square game, classical approaches and why it is impossible to
systematically win the game classically, how and why the quantum
strategy works, and how to implement it. We also briefly discuss how
the game translates to the proof of incompatibility of a
noncontextual hidden-variable theory. Then, in
Section~\ref{sec:extending}, we describe a generalization of games
that follow the same style of the magic square game, given
by Arkhipov~\cite{arkhipov:2012}. Finally, Section~\ref{sec:conc} concludes the
presentation.

@@

As seen in Section~\ref{sec:classic-sol}, the \emph{magic} square is
called this way because, under classical assumptions, there is no such
a square: it is impossible to construct a \(3 \times 3\) matrix filled
with \(\pm 1\)'s, with the constraints that the product of every row
is \(+1\) and the product of every column is \(-1\). We can, however,
construct a ``quantum magic'' square. Figure~\ref{fig:quantum} shows
the \(3 \times 3\) grid that Alice and Bob can use to win the magic
square game systematically.  Notice that the eigenvalues of the
observables at each cell are \(\pm 1\). Furthermore, the product of
every row is \(+I\) and the product of every column is \(-I\).  The
quantum strategy works as follows: Alice measures all the observables
from the \(i\)-th row of the predefined matrix. She fills each cell
with the result of each measurement. Similarly, Bob measures all the
observables in the \(j\)-th column that was assigned to him, and fills
each of his cells with the outcomes of each
measurement. Example~\ref{ex:quantum-sol} depicts a round of the game.

@@

    \ket{\psi}_{A1} =  \frac{1}{\sqrt{2}}(\ket{0000} + \ket{1010}),

@@

  where the subscript \(A1\) denotes the state after Alice's first

@@

    \ket{\psi}_{A2} =  \ket{1010}.

@@

  \(\ket{\psi}_{A3} = \ket{\psi}_{A2}\).  Alice, then, fills the first

@@

  \(\ket{\psi}_{A3}\), is \(-1\) ---~which matches Alice's answer~---

@@

  \(\ket{\psi}_{B1} = \ket{\psi}_{A3}\). Moving on to the second cell,

@@

    \ket{\psi}_{B2} =  \frac{1}{\sqrt{2}}(\ket{1010} + \ket{1011}).

@@

 change, i.e.  \(\ket{\psi}_{B3} = \ket{\psi}_{B2}\). Therefore, Bob

@@

\subsection{Formal Proof}\label{sec:msquare-proof}
To prove that the quantum solution indeed works, we must demonstrate
two fundamental properties. First, the product of the outcomes of the
three measurements on each row (equivalently, column) is equal to 1
(equiv. -1). Second, the outcome of Alice's measurement on the
intersection is always equal to the outcome of
Bob's. Lemma~\ref{lem:product} formalizes the product property.

@@

\begin{proof}
  \label{proof:product}
  First, notice that \(X^{2} = Z^{2} = Y^{2} = I\), \(XZ = \ci{}Y\)
  and \(ZX = -\ci{}Y\) (i.e. \(X\) and \(Z\) anticommute), and,
  similarly, \(XY = \ci{}Z\) and \(YX = -\ci{}Z\). Using these
  properties, we can see that the product of every row (equiv. column)
  is the identity \(I\) (equiv. \(-I\)), regardless of the order of
  the three observables.  That is, the three observables of every row
  and every column mutually commute (or, in other words, they are
  compatible).  Consequently, for every row and every column, it is
  possible to find a basis of eigenvectors that are common to the
  three observables, meaning that they can be diagonalized
  simultaneously. Tables~\ref{tab:eigenv-rows} and \ref{tab:eigenv-cols} show
  these common eigenvectors. Let \(M_{i, j}\) be the observables at
  each cell.  Then, for every row \(i\) (equiv. column \(j\)), we have
  \begin{align}
    M_{i, 0} M_{i, 1} M_{i, 2}
    &= (P_{i} \Lambda_{i, 0} P_{i}^{-1}) (P_{i}\Lambda_{i, 1}P_{i}^{-1}) (P_{i}\Lambda_{i, 2}P_{i}^{-1})
      \nonumber \\
    &= P_{i}(\Lambda_{i, 0} \Lambda_{i, 1} \Lambda_{i, 2})P_{i}^{-1} \nonumber \\
    &= P_{i}\Lambda_{i}P_{i}^{-1},
  \end{align}
  where \(P_{i}\) is the matrix whose columns are the common
  eigenvectors and \(\Lambda_{i}\) is the matrix whose diagonal is
  formed by the products of the eigenvalues of the observables,
  associated with the same eigenvector. What this essentially means is
  that any measurement \(M_{i, j}\) yields one of the eigenvalues
  \(\lambda\) in the diagonal of \(\Lambda_{i, j}\) and projects the
  state onto the \(\lambda\)-eigenspace. That is, it collapses the
  state to a linear combination of the two shared eigenvectors
  \(\ket{\lambda}_{0}\) and \(\ket{\lambda}_{1}\) in the
  \(\lambda\)-eigenspace. Then, the second measurement will collapse
  the state to either \(\ket{\lambda}_{0}\) or \(\ket{\lambda}_{1}\),
  eigenvectors common to the three observables.  Consequently, the
  third measurement will not change the state any further. Therefore,
  the product of the three outcomes will be the product of the
  eigenvalues associated with either \(\ket{\lambda}_{0}\) or
  \(\ket{\lambda}_{1}\), which is one of the entries in the diagonal
  of \(\Lambda_{i}\). But, notice that
  \(P_{i}\Lambda_{i}P_{i}^{-1} = I\); thus, \(\Lambda_{i} = I\) and
  the only possible value for the product is \(1\) (equivalently
  \(-1\) for columns). \qed
\end{proof}

@@

\begin{proof}
  To prove that Alice and Bob agree at the intersection, it suffices
  to look to the eigenvectors shared by each set of mutually commuting
  operators, shown in Tables~\ref{tab:eigenv-rows} and
  \ref{tab:eigenv-cols}.  Notice that, regardless of the row assigned
  to Alice, the state of her subsystem after her measurements is
  always one of the eigenvectors in that row. This state is always a
  linear combination of one of Bob's eigenspaces for the cell in the
  intersection (the same applies if we consider first Bob than Alice).
  Take, for instance, the second row and first column. Suppose that
  Alice's measurements collapsed her qubits to
  \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\).
  This state can be written as
  \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{10}) -
  (\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{11})\), a linear
  combination of the \(-1\)-eigenspace depicted in
  Table~\ref{tab:eigenv-cols} (column 0, row 1).  What is left is to
  show that Bob's state will be exactly the same as Alice's, implying
  that Bob shall observe the same result. This follows from the fact
  that the initial state is already symmetric (the first qubit of
  Alice is equal to the first qubit of Bob; the same is true for their
  second qubits) and the symmetry is preserved by any measurement
  performed by Alice and Bob. For the first row, it is easy to see.
  The others are trickier, but it all boils down to doing the
  calculations.  Consider, for instance, the second row, and suppose
  that the outcomes were \(-1\), \(-1\) and \(+1\), so that Alice's
  state collapsed to
  \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} +
  \ket{11})\). The state after the first measurement is
  \begin{align}
    &\frac{1}{2\sqrt{2}} \Bigl(
    (\ket{00} - \ket{10}) \ket{00} +
    (\ket{01} - \ket{11}) \ket{01} +
    (\ket{10} - \ket{00}) \ket{10} +
    (\ket{11} - \ket{01}) \ket{11}
    \Bigr) \nonumber \\
    \equiv\;
    & \frac{1}{2\sqrt{2}} \Bigl(
      \ket{00} (\ket{00} - \ket{10}) +
      \ket{01} (\ket{01} - \ket{11}) +
      \ket{10} (\ket{10} - \ket{00}) +
      \ket{11} (\ket{11} - \ket{01})
    \Bigr).
  \end{align}
  And, the state after the second measurement is
  \begin{alignat}{2}
    &\frac{1}{4} \Bigl(
      &&(\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{00} -
        (\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{01} - \nonumber \\
    & &&(\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{10} +
      (\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{11}
    \Bigr) \nonumber \\
    \equiv\;
    & \frac{1}{4} \Bigl(
      &&\ket{00} (\ket{00} - \ket{01} - \ket{10} + \ket{11}) -
        \ket{01} (\ket{00} - \ket{01} - \ket{10} + \ket{11}) - \nonumber \\
    & &&\ket{10} (\ket{00} - \ket{01} - \ket{10} + \ket{11}) +
         \ket{11} (\ket{00} - \ket{01} - \ket{10} + \ket{11})
         \Bigr).
  \end{alignat}
  The calculations for the other rows and columns are similar, so we omitted them.
  \qed

@@

  \begin{theorem}[The Mermin-Peres Magic Square Game Is Winnable]
    \label{theo:quantum-wins}
    There exists a quantum strategy for the Mermin-Peres magic square
    game, which consists of allowing Alice and Bob exchanging
    entangled qubits \emph{before} the game begins, that wins with
    certainty every round.
  \end{theorem}
\end{proof}

@@

{\renewcommand{\arraystretch}{2}
  \begin{figure}
    \centering
    \[\begin{array}{|*{2}{>{\quad}c<{\quad}|}>{\quad}l<{\quad}|}
        \hhline{---}
        (I \otimes I) (I \otimes Z) (I \otimes I) & (I \otimes I) (Z \otimes I) (I \otimes I) & \cnot (I \otimes Z) \cnot
        \\ \hhline{---}
        (H \otimes I) (Z \otimes I) (H \otimes I) & (I \otimes H) (I \otimes Z) (I \otimes H) & (H \otimes H) (Z \otimes Z) (H \otimes H)
        \\ \hhline{---}
        (H \otimes Y) (Z \otimes Z) (H \otimes Y) & (Y \otimes H) (Z \otimes Z) (Y \otimes H) &
                                                                                                (S \otimes S) (X \otimes X) (S^{*} \otimes S^{*}) 
        \\ \hhline{---}
      \end{array}\]
    \caption{Unitary transformations required for measuring in the
      different basis. The actual basis measured is the middle
      term of each cell, which, after expanding, is either
      \(Z \otimes I\) or \(I \otimes Z\). For example, in the last
      cell, \(X \otimes X\) evaluates to
      \((H \otimes H) (Z \otimes Z) (H \otimes H)\).
      \(Z \otimes Z\), in turn, becomes \(\cnot (I \otimes Z) \cnot\), meaning that
      we measure the second qubit in the computational basis.\label{fig:change-basis}}
  \end{figure}}

@@

As seen in the Section~\ref{sec:msquare-proof}, the operators on each
row and column are compatible. That is, for any row and any column,
the observables pairwise commute. This means that they can be
simultaneously diagonalized by the same eigenvectors. It turns out
that the simultaneous measurement of compatible operators is
equivalent to the measurement of a single nondegenerate
operator~\cite{peres:1997}. That is, instead of performing three
measurements, one for each cell, Alice and Bob could perform a single
measurement each, whose answers would tell them to which of the four
common eigenvectors their qubits would have collapsed to, had they
performed the individual measurements. Based on this, they could fill
each cell with the eigenvalue that corresponds to that eigenvector. To
construct these single measurements for each row and column, it
suffices to take the projectors onto the eigenvectors shared by the
observables. Example~\ref{ex:sim-meas} further illustrates this idea.

\begin{tcbexample}{Simultaneous Measurement}{sim-meas}
  Consider, for instance, the first row of the quantum solution for
  the magic square game, depicted in Figure~\ref{fig:quantum}. The
  observables in this row are \(I \otimes Z\), \(Z \otimes I\), and
  \(Z \otimes Z\). The eigenvectors common to these operators are
  \ket{00}, \ket{01}, \ket{10}, and \ket{11}. Alice, then, could
  simply construct an observable
  \[M = \ketbra{00}{00} + 2 \ketbra{01}{01} + 3 \ketbra{10}{10} + 4
    \ketbra{11}{11},\] which corresponds to the diagonal matrix
  \begin{equation*}
    M = \begin{pmatrix}
          1 & 0 & 0 & 0 \\
          0 & 2 & 0 & 0 \\
          0 & 0 & 3 & 0 \\
          0 & 0 & 0 & 4
    \end{pmatrix}.
  \end{equation*}
  By measuring \(M\) on her qubits, she would observe (with
  probability \(\nicefrac{1}{4}\)) the outcomes \(1\), \(2\), \(3\), or
  \(4\) , which uniquely identifies one of the four eigenvectors
  \ket{00}, \ket{01}, \ket{10}, or \ket{11}. Consequently, she would
  know the eigenvalues associated with the eigenvector ``observed'',
  and would be able to correctly fill the cells of the first row. For
  example, outcome \(3\) corresponds to \ket{10}. Hence, if she
  observes \(3\), she fills the first row with \(\{+1, -1, -1\}\).
\end{tcbexample}

@@

Notice that the generalization above differs a bit from the magic
square game seen in Section~\ref{sec:magic-square}, where Alice
receives a hyperedge. This modification generalizes to
arrangements that do not share the property exhibited by the magic
square that its lines can be split into two disjoint sets (rows and
columns). In this sense, one can simply understand the magic square
game as a combination of two rounds. In the first ``half'' of the
round, Charlie sends the vertex \(u\) to Alice and the line \(e\) to
Bob. In the second half, Charlie sends \(u\) to Bob, but
\emph{another} line \(e' \neq e\) to Alice.

@@

  Following the proof of Theorem~\ref{theo:main}, we assume that the
  vertices with a correspondence in the \(K_{3, 3}\) graph are
  labelled in the same way, and the remaining are labelled with
  \(+I\).  To construct a quantum realization of the Petersen graph,
  we first look for simples paths that correspond to edges in
  \(K_{3, 3}\). For example, the edge \((e_{0}, e_{1})\) in Petersen
  corresponds exactly to the edge \((e'_{0}, e'_{3})\) in
  \(K_{3, 3}\), so we assign the operator \(I \otimes Z\) to
  it. Similarly, the path \((e_{0}, e_{4}, e_{3})\) in Petersen
  corresponds to the edge \((e'_{0}, e'_{4})\) in \(K_{3, 3}\), so we
  assign the operator \(Z \otimes I\) to both edges \((e_{0}, e_{4})\)
  and \((e_{4}, e_{3})\). We keep doing this for every path that has a
  correspondence in the \(K_{3, 3}\) graph. Then, we label the
  remaining edges with \(+I\). Figure~\ref{fig:petersen-final} shows
  the quantum realization constructed for the Petersen graph.

@@

\section{Conclusion}\label{sec:conc}

>>>>

\maketitle
\begin{abstract}
This paper explores the phenomenon of quantum pseudo-telepathy, a form of communication that exhibits properties resembling telepathy by leveraging aspects of the quantum realm. Specifically, the focus is on the Mermin-Peres magic square game, which exemplifies quantum pseudo-telepathy and provides a simplified proof for the Kochen-Specker theorem. The paper begins by discussing various examples of quantum pseudo-telepathy games and their incompatibility with classical winning strategies, highlighting the necessity of prior entanglement between players. Additionally, it delves into the intricacies of the magic square game, classical approaches, the impossibility of consistent classical winning, and the rationale behind the successful implementation of a quantum strategy. Moreover, it explores the connection between the game and the proof of the incompatibility of noncontextual hidden-variable theories. Furthermore, a generalization of games similar to the magic square, proposed by Arkhipov, is presented. Ultimately, through this investigation, the paper sheds light on the fascinating realm of quantum pseudo-telepathy and its implications for our understanding of classical physics and quantum mechanics.
\end{abstract}

@@

\paragraph{Outline of this paper.}
In Section~\ref{sec:magic-square}, we detail the intrinsics of the
magic square game, classical approaches and why it is impossible to
systematically win the game classically, how and why the quantum
strategy works, and how to implement it. We also briefly discuss how
the game translates to the proof of incompatibility of a
noncontextual hidden-variable theory. Then, in
Section~\ref{sec:extending}, we describe a generalization of games
that follow the same style of the magic square game, given
by Arkhipov~\cite{arkhipov:2012}. Finally, Section~\ref{sec:conc} concludes this report.

@@

As seen in Section~\ref{sec:classic-sol}, the \emph{magic} square is
called this way because, under classical assumptions, there is no such
a square: it is impossible to construct a \(3 \times 3\) matrix filled
with \(\pm 1\)'s, with the constraints that the product of every row
is \(+1\) and the product of every column is \(-1\). We can, however,
construct a ``quantum magic'' square. Figure~\ref{fig:quantum} shows
the \(3 \times 3\) grid that Alice and Bob can use to win the magic
square game systematically.  Notice that the eigenvalues of the
observables at each cell are \(\pm 1\). Furthermore, the product of
every row is \(+I\) and the product of every column is \(-I\).  The
quantum strategy works as follows: Alice measures all the observables
from the \(i\)-th row of the predefined matrix. She fills each cell
with the result of each measurement. Similarly, Bob measures all the
observables in the \(j\)-th column that was assigned to him, and fills
each of his cells with the outcomes of each measurement. (It is worth
to point out that the order of their measurements is not important.)
Example~\ref{ex:quantum-sol} depicts a round of the game.

@@

    \ket{\psi}_{A0} =  \frac{1}{\sqrt{2}}(\ket{0000} + \ket{1010}),

@@

  where the subscript \(A0\) denotes the state after Alice's first

@@

    \ket{\psi}_{A1} =  \ket{1010}.

@@

  \(\ket{\psi}_{A2} = \ket{\psi}_{A1}\).  Alice, then, fills the first

@@

  \(\ket{\psi}_{A2}\), is \(-1\) ---~which matches Alice's answer~---

@@

  \(\ket{\psi}_{B0} = \ket{\psi}_{A2}\). Moving on to the second cell,

@@

    \ket{\psi}_{B1} =  \frac{1}{\sqrt{2}}(\ket{1010} + \ket{1011}).

@@

 change, i.e.  \(\ket{\psi}_{B2} = \ket{\psi}_{B1}\). Therefore, Bob

@@

\subsection{Formal Proof}\label{sec:msquare-proof}
To prove that the quantum solution indeed works, we must demonstrate
two fundamental properties. First, the product of the outcomes of the
three measurements on each row (equivalently, column) is equal to 1
(equivalently, -1). Second, the outcome of Alice's measurement on the
intersection is always equal to the outcome of
Bob's. Lemma~\ref{lem:product} formalizes the product property.

@@

\begin{proof}
  \label{proof:product}
  First, notice that \(X^{2} = Z^{2} = Y^{2} = I\), \(XZ = \ci{}Y\)
  and \(ZX = -\ci{}Y\) (i.e. \(X\) and \(Z\) anticommute), and,
  similarly, \(XY = \ci{}Z\) and \(YX = -\ci{}Z\). Using these
  properties, we can see that the product of every row (equiv. column)
  is the identity \(I\) (equiv. \(-I\)), regardless of the order of
  the three observables.  That is, the three observables of every row
  and every column mutually commute (or, in other words, they are
  compatible).  Consequently, for every row and every column, it is
  possible to find a basis of eigenvectors that are common to the
  three observables, meaning that they can be diagonalized
  simultaneously. Tables~\ref{tab:eigenv-rows} and \ref{tab:eigenv-cols} show
  these common eigenvectors. Let \(M_{i, j}\) be the observables at
  each cell.  Then, for every row \(i\) (equiv. column \(j\)), we have
  \begin{align}
    M_{i, 0} M_{i, 1} M_{i, 2}
    &= (P_{i} \Lambda_{i, 0} P_{i}^{-1}) (P_{i}\Lambda_{i, 1}P_{i}^{-1}) (P_{i}\Lambda_{i, 2}P_{i}^{-1})
      \nonumber \\
    &= P_{i}(\Lambda_{i, 0} \Lambda_{i, 1} \Lambda_{i, 2})P_{i}^{-1} \nonumber \\
    &= P_{i}\Lambda_{i}P_{i}^{-1},
  \end{align}
  where \(P_{i}\) is the matrix whose columns are the common
  eigenvectors and \(\Lambda_{i}\) is the matrix whose diagonal is
  formed by the products of the eigenvalues of the observables,
  associated with the same eigenvector. What this essentially means is
  that any measurement \(M_{i, j}\) yields one of the eigenvalues
  \(\lambda\) in the diagonal of \(\Lambda_{i, j}\) and projects the
  state onto the \(\lambda\)-eigenspace. That is, it collapses the
  state to a linear combination of the two shared eigenvectors
  \(\ket{\lambda}_{0}\) and \(\ket{\lambda}_{1}\) in the
  \(\lambda\)-eigenspace. Then, the second measurement will collapse
  the state to either \(\ket{\lambda}_{0}\) or \(\ket{\lambda}_{1}\),
  eigenvectors common to the three observables.  Consequently, the
  third measurement will not change the state any further. Therefore,
  the product of the three outcomes will be the product of the
  eigenvalues associated with either \(\ket{\lambda}_{0}\) or
  \(\ket{\lambda}_{1}\), which is one of the entries in the diagonal
  of \(\Lambda_{i}\). But, notice that
  \(P_{i}\Lambda_{i}P_{i}^{-1} = I\); thus, \(\Lambda_{i} = I\) and
  the only possible value for the product is \(1\) (equivalently,
  \(-1\) for columns). \qed
\end{proof}

@@

\begin{proof}
  To prove that Alice and Bob agree at the intersection, it suffices
  to look to the eigenvectors shared by each set of mutually commuting
  operators, shown in Tables~\ref{tab:eigenv-rows} and
  \ref{tab:eigenv-cols}.  Notice that, regardless of the row assigned
  to Alice, the state of her subsystem after her measurements is
  always one of the eigenvectors in that row. This state is always a
  linear combination of one of Bob's eigenspaces for the cell in the
  intersection (the same applies if we consider first Bob than Alice).
  Take, for instance, the second row and first column. Suppose that
  Alice's measurements collapsed her qubits to
  \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\).
  This state can be written as
  \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{10}) -
  (\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{11})\), a linear
  combination of the \(-1\)-eigenspace depicted in
  Table~\ref{tab:eigenv-cols} (column 0, row 1).  What is left is to
  show that Bob's state will be exactly the same as Alice's, implying
  that Bob shall observe the same result. This follows from the fact
  that the initial state is already symmetric (the first qubit of
  Alice is equal to the first qubit of Bob; the same is true for their
  second qubits) and the symmetry is preserved by any measurement
  performed by Alice and Bob. For the first row, this is easy to see.
  The others are trickier, but it all boils down to doing the
  calculations.  Consider, for instance, the second row, and suppose
  that the outcomes were \(-1\), \(-1\) and \(+1\), so that Alice's
  state collapsed to
  \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} +
  \ket{11})\). The complete state after the first measurement is
  \begin{align}
    &\frac{1}{2\sqrt{2}} \Bigl(
    (\ket{00} - \ket{10}) \ket{00} +
    (\ket{01} - \ket{11}) \ket{01} +
    (\ket{10} - \ket{00}) \ket{10} +
    (\ket{11} - \ket{01}) \ket{11}
    \Bigr) \nonumber \\
    \equiv\;
    & \frac{1}{2\sqrt{2}} \Bigl(
      \ket{00} (\ket{00} - \ket{10}) +
      \ket{01} (\ket{01} - \ket{11}) +
      \ket{10} (\ket{10} - \ket{00}) +
      \ket{11} (\ket{11} - \ket{01})
    \Bigr).
  \end{align}
  And, the state after the second measurement is
  \begin{alignat}{2}
    &\frac{1}{4} \Bigl(
      &&(\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{00} -
        (\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{01} - \nonumber \\
    & &&(\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{10} +
      (\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{11}
    \Bigr) \nonumber \\
    \equiv\;
    & \frac{1}{4} \Bigl(
      &&\ket{00} (\ket{00} - \ket{01} - \ket{10} + \ket{11}) -
        \ket{01} (\ket{00} - \ket{01} - \ket{10} + \ket{11}) - \nonumber \\
    & &&\ket{10} (\ket{00} - \ket{01} - \ket{10} + \ket{11}) +
         \ket{11} (\ket{00} - \ket{01} - \ket{10} + \ket{11})
         \Bigr).
  \end{alignat}
  The calculations for the other rows and columns are similar, so we omitted them.
  \qed

@@

  \begin{theorem}[The Mermin-Peres Magic Square Game Is Winnable]
    \label{theo:quantum-wins}
    There exists a quantum strategy for the Mermin-Peres magic square
    game, which consists of allowing Alice and Bob to exchange
    entangled qubits \emph{before} the game begins, that wins with
    certainty every round.
  \end{theorem}
\end{proof}

@@

{\renewcommand{\arraystretch}{2}
  \begin{figure}
    \centering
    \[\begin{array}{|*{2}{>{\quad}c<{\quad}|}>{\quad}l<{\quad}|}
        \hhline{---}
        (I \otimes I) (I \otimes Z) (I \otimes I) & (I \otimes I) (Z \otimes I) (I \otimes I) & \cnot (I \otimes Z) \cnot
        \\ \hhline{---}
        (H \otimes I) (Z \otimes I) (H \otimes I) & (I \otimes H) (I \otimes Z) (I \otimes H) & (H \otimes H) (Z \otimes Z) (H \otimes H)
        \\ \hhline{---}
        (H \otimes Y) (Z \otimes Z) (H \otimes Y) & (Y \otimes H) (Z \otimes Z) (Y \otimes H) &
                                                                                                (S \otimes S) (X \otimes X) (S^{*} \otimes S^{*}) 
        \\ \hhline{---}
      \end{array}\]
    \caption{Unitary transformations required for measuring in
      different bases. The actual basis measured is the middle
      term of each cell, which, after expanding, is either
      \(Z \otimes I\) or \(I \otimes Z\). For example, in the last
      cell, \(X \otimes X\) evaluates to
      \((H \otimes H) (Z \otimes Z) (H \otimes H)\).
      \(Z \otimes Z\), in turn, becomes \(\cnot (I \otimes Z) \cnot\), meaning that
      we measure the second qubit in the computational basis.\label{fig:change-basis}}
  \end{figure}}

@@

As seen in Section~\ref{sec:msquare-proof}, the operators on each
row and column are compatible. That is, for any row and any column,
the observables pairwise commute. This means that they can be
simultaneously diagonalized by the same eigenvectors. It turns out
that the simultaneous measurement of compatible operators is
equivalent to the measurement of a single nondegenerate
operator~\cite{peres:1997}. That is, instead of performing three
measurements, one for each cell, Alice and Bob could perform a single
measurement each, whose answers would tell them to which of the four
common eigenvectors their qubits would have collapsed to, had they
performed the individual measurements. Based on this, they could fill
each cell with the eigenvalue that corresponds to that eigenvector. To
construct these single measurements for each row and column, it
suffices to take the projectors onto the eigenvectors shared by the
observables. Example~\ref{ex:sim-meas} further illustrates this idea.

\begin{tcbexample}{Simultaneous Measurement}{sim-meas}
  Consider, for instance, the first row of the quantum solution for
  the magic square game, depicted in Figure~\ref{fig:quantum}. The
  observables in this row are \(I \otimes Z\), \(Z \otimes I\), and
  \(Z \otimes Z\). The eigenvectors common to these operators are
  \ket{00}, \ket{01}, \ket{10}, and \ket{11}. Alice, then, could
  simply construct an observable
  \[M = \ketbra{00}{00} + 2 \ketbra{01}{01} + 3 \ketbra{10}{10} + 4
    \ketbra{11}{11},\] which corresponds to the diagonal matrix
  \begin{equation*}
    M = \begin{pmatrix}
          1 & 0 & 0 & 0 \\
          0 & 2 & 0 & 0 \\
          0 & 0 & 3 & 0 \\
          0 & 0 & 0 & 4
    \end{pmatrix}.
  \end{equation*}
  By measuring \(M\) on her qubits, she would observe (with
  probability \(\nicefrac{1}{4}\)) the outcomes \(1\), \(2\), \(3\), or
  \(4\), which uniquely identifies one of the four eigenvectors
  \ket{00}, \ket{01}, \ket{10}, or \ket{11}. Consequently, she would
  know the eigenvalues associated with the eigenvector ``observed'',
  and would be able to correctly fill the cells of the first row. For
  example, outcome \(3\) corresponds to \ket{10}. Hence, if she
  observes \(3\), she fills the first row with \(\{+1, -1, -1\}\).
\end{tcbexample}

@@

Notice that the generalization above differs a bit from the magic
square game seen in Section~\ref{sec:magic-square}, where Alice
receives a hyperedge. This modification generalizes to
arrangements that do not share the property exhibited by the magic
square that its lines can be split into two disjoint sets (rows and
columns). In this sense, one can simply understand the magic square
game as a combination of two rounds. In the first ``half'' of the
round, Charlie sends the vertex \(u\) to Alice and the line \(e\) to
Bob. In the second half, Charlie sends \(u\) to Bob, but the other
line \(e'\) containing \(u\) to Alice.

@@

  Following the proof of Theorem~\ref{theo:main}, we assume that the
  vertices with a correspondence in the \(K_{3, 3}\) graph are
  labelled in the same way, and the remaining are labelled with
  \(+I\).  To construct a quantum realization of the Petersen graph,
  we first look for simple paths that correspond to edges in
  \(K_{3, 3}\). For example, the edge \((e_{0}, e_{1})\) in Petersen
  corresponds exactly to the edge \((e'_{0}, e'_{3})\) in
  \(K_{3, 3}\), so we assign the operator \(I \otimes Z\) to
  it. Similarly, the path \((e_{0}, e_{4}, e_{3})\) in Petersen
  corresponds to the edge \((e'_{0}, e'_{4})\) in \(K_{3, 3}\), so we
  assign the operator \(Z \otimes I\) to both edges \((e_{0}, e_{4})\)
  and \((e_{4}, e_{3})\). We keep doing this for every path that has a
  correspondence in the \(K_{3, 3}\) graph. Then, we label the
  remaining edges with \(+I\). Figure~\ref{fig:petersen-final} shows
  the quantum realization constructed for the Petersen graph.

@@

\section{Conclusion}\label{sec:conc}
In this work, we described the two-players cooperative quantum magic
game known as the magic square game, that exhibits the so-called
property of pseudo-telepathy. In other words, it is a game that is
impossible to systematically win under classical assumptions (i.e.\
when restricted to a classical solution, if the players are always
winning, the referee can suspect that they are somehow cheating and
communicating), but that there exists a quantum strategy that wins
every round with certainty, which gives the impression that some sort
of communication is going on (hence ``pseudo-telepathy'').
We described the classical and quantum strategies, showed why
the quantum approach works, and how to implement it with
quantum circuits. We also briefly discussed the connection between the
magic square game and the Kochen-Specker theorem, which states the
incompatibility between a quantum mechanics model that is both
noncontextual and deterministic.

We concluded by describing a generalization of games that follow the same
style of the magic square, also known as Mermin-style games, given by
Arkhipov~\cite{arkhipov:2012}. In this generalization, the quantum
games are represented by hypergraphs whose hyperedges encode the
constraints of the game and whose vertices must be labelled by the
players in a way that this labelling respects those constraints. In the
case of the magic square, the hyperedges are the three rows and three
columns, and the vertices are each cell of the grid. Arkhipov showed
in his work that there exists a subset of these games that are
``magical'' in the sense that they cannot be won classically, but they
admit a quantum strategy. This quantum solution, as in the magic
square case, consists of the two players sharing a symmetric,
entangled state. Furthermore, the arrangement on which these games are
played can be characterized in terms of the (non)planarity of the
corresponding intersection graphs: the arrangement is magic if, and
only if, its intersection graph is nonplanar.
